\mytitle

### 2021-11-05 main.tex
Editted to end of Sect 2.

The goal in the wind farm layout optimization (WFLO)
problem~\cite{MOSETTI1994105} is to locate wind turbines within a
predefined area to maximize the total power harvested from the wind
stream.  While physical considerations based on the diameter of the
blades prevent turbines being placed too close to each other, turbine
location decisions influence the total power production due to
interference effects (i.e., wakes) generated by upstream turbines.
These inter-turbine effects are best captured by Jensen's wake model~\cite{jensen1983note} when superimposed
using a sum-of-squares expression~\cite{Zhang2014}. However,
this wake modeling yields intractable optimization problems
that must be approximated using either quadratic or linear functions~\cite{turner2014new}.
An alternative formulation of WFLO relies on a less accurate wake model, using linear superpositioning
to capture multiple wakes~\cite{donovan2005wind}.
The latter can be captured using quadratic
constraints and objective functions. However, exact optimization
approaches that have been proposed for the alternative WFLO formulation~\cite{Zhang2014,kuo2016wind,donovan2005wind,fagerfjall2010optimizing,archer2011wind,sorkhabi2018constrained}
represent the quadratic relations using approximate linear models,
%that approximate wake dependencies,
as solving quadratic programming problems
is computationally challenging compared to linear models.

@@

\item We show through numerical experiments that, when solved with specialized hardware (Fujitsu's Digital Annealer), \textcolor{purple}{the QUBO model finds solutions competitive with the state of the art in 1 second, representing a computational speed-up of two to three orders of magnitude compared to software based methods.} Such a short runtime enables an interactive wind farm design cycle.

@@

We assume that the number of identical turbines to be placed is known 
in advance and denoted by $m$. To place these $m$ turbines, 
we must consider two types of interference effect: \emph{proximity constraints} and \emph{wakes}.
In what follows, we explain the two effects using a toy example with an 
$8\times8$ grid (see Figure~\ref{fig:field_model}).

@@

Zhang et al.\ \cite{Zhang2014} developed a constraint programming (CP) approach to the problem variation presented above. CP is an optimization technique that has grown from the AI literature that does not make the assumptions on the functional form of the constraints or objective \cite{rossi2006handbook}. The authors compared existing MILP and QP models to their approach for directly optimizing the SS objective and showed that, while promising for smaller problems, applying CP turned out to be computationally intractable for the larger standard WFLO benchmarks.

@@

The first attempt to address these limitations 
was made using a local search approach~\cite{ozturk2004heuristic}. 
The approach does not guarantee optimality, 
yet it circumvents the termination and feasibility checking issues of the evolutionary
methods. The local search attempts to apply either move, remove or add actions given an incumbent 
feasible solution. When a turbine is moved, removed or added, the new solution is evaluated. The procedure terminates 
when a stopping criteria is reached.
The main limitation of this approach 
%~\cite{ozturk2004heuristic}
is that it cannot perform an action 
that leads to an infeasible state and, therefore, often quickly converges to a sub-optimal solution (local optimum) 
that can potentially be much lower quality than the globally optimal solution~\cite{rivas2009solving}.

To overcome this limitation, Rivas et al.\ \cite{rivas2009solving} used simulated annealing (SA), 
a neighborhood search method that allows visits to infeasible solutions. 
SA creates a well-connected solution space that allows the algorithm to escape 
local optima. The SA method was shown to be superior to the approach of Ozturk \& Norman~\cite{ozturk2004heuristic} 
and to the genetic method proposed in Grady et al.\ \cite{grady2005placement}. A drawback of the SA approach 
is its ad-hoc nature. The various components of the algorithm
 must be tailored to the problem at hand and, as a result, small adjustments of the WFLO setting
 (e.g., adding noise considerations), would require major changes to the SA implementation. 
Additional methods and experimental comparisons between various approximate algorithms are available in Samorani~\cite{samorani2013wind}.

>>>>

The goal in the wind farm layout optimization (WFLO)
problem~\cite{MOSETTI1994105} is to locate wind turbines within a
predefined area to maximize the total power harvested from the wind
stream.  While physical considerations based on the diameter of the
blades prevent turbines being placed too close to each other, turbine
location decisions influence the total power production due to
interference effects (i.e., wakes) generated by upstream turbines.
These inter-turbine effects are best captured by Jensen's wake model~\cite{jensen1983note} when superimposed
using a sum-of-squares expression~\cite{Zhang2014}. However,
this wake modeling yields intractable optimization problems
that have been approximated using either quadratic or linear functions~\cite{turner2014new}.
An alternative formulation of WFLO relies on a less accurate wake model, using linear superpositioning
to capture multiple wakes~\cite{donovan2005wind}.
The latter can be captured using quadratic
constraints and objective functions. However, exact optimization
approaches that have been proposed for the alternative WFLO formulation~\cite{Zhang2014,kuo2016wind,donovan2005wind,fagerfjall2010optimizing,archer2011wind,sorkhabi2018constrained}
represent the quadratic relations using approximate linear models,
%that approximate wake dependencies,
as solving quadratic programming problems
is computationally challenging compared to linear models.

@@

\item We show through numerical experiments that, when solved with specialized hardware (Fujitsu's Digital Annealer), the QUBO model finds solutions competitive with the state of the art in one second, representing a computational speed-up of two to three orders of magnitude compared to software based methods. Such a short runtime enables an interactive wind farm design cycle.

@@

As is common, we assume that the number of identical turbines to be placed is known 
in advance and denoted by $m$. To place these $m$ turbines, 
we must consider two types of interference effect: \emph{proximity constraints} and \emph{wakes}.
In what follows, we explain the two effects using a toy example with an 
$8\times8$ grid (see Figure~\ref{fig:field_model}).

@@

Zhang et al.\ \cite{Zhang2014} developed a constraint programming (CP) approach to the problem variation presented above. CP is an optimization technique that has grown from the AI literature that does not make the assumptions on the functional form of the constraints or objective \cite{rossi2006handbook}. The authors compared existing MILP and QP models to their approach for directly optimizing the SS objective and showed that, while promising for smaller problems, applying CP was computationally intractable for the larger standard WFLO benchmarks.

@@

The first attempt to address these limitations 
was made using a local search approach~\cite{ozturk2004heuristic}. 
The approach does not guarantee optimality, 
yet it circumvents the termination and feasibility checking issues of the evolutionary
methods. The local search attempts to apply either move, remove, or add actions given an incumbent 
feasible solution. When a turbine is moved, removed, or added, the new solution is evaluated. The procedure terminates 
when a stopping criteria is reached.
The main limitation of this approach 
%~\cite{ozturk2004heuristic}
is that it cannot perform an action 
that leads to an infeasible state and, therefore, often quickly converges to a sub-optimal solution (local optimum) 
that can potentially be much lower quality than the globally optimal solution~\cite{rivas2009solving}.

To overcome this limitation, Rivas et al.\ \cite{rivas2009solving} used simulated annealing (SA), 
a neighborhood search method that creates a connected solution space that allows the algorithm to escape 
local optima. The SA method was shown to be superior to the approach of Ozturk \& Norman~\cite{ozturk2004heuristic} 
and to the genetic method proposed in Grady et al.\ \cite{grady2005placement}. A drawback of the SA approach 
is its ad-hoc nature. The various components of the algorithm
 must be tailored to the problem at hand and, as a result, small adjustments of the WFLO setting
 (e.g., adding noise considerations), would require major changes to the SA implementation. 
Additional methods and experimental comparisons between various approximate algorithms are available in Samorani~\cite{samorani2013wind}.
